A Bidirected String Graph Model for Genome Assembly

### 2012-12-17 presentation/paper.tex
paper: fix typo

Fortunately, there does exist a way to solve a bidirected flow problem by
mapping it to a directed flow problem by using the directed equivalent of the
bidirected graph, described in \Subsection{subsec:directed}.  However, the
calculated flow on a directed edge between, for example, two vertices $f.E \to
g.E$ is not guaranteed to be the same as the flow on $g.B \to f.B$, the edge
that corresponds to the other direction of the implied bidirected edge.  This
problem can be worked around by taking the average of the two counts and using
this as the flow on the bidirected edge.  This approximation is equivalent to
performing monotonization on the binet matrix that represents the linear program
reduction of bidirected flow; this produces a totally unimodular matrix that
represents a linear program that can be solved to find an integal flow that is
at worst a 2-approximation to the optimal integral flow on the bidirected
graph\cite{Medvedev2009}\cite{Hochbaum2004}.

>>>>

Fortunately, there does exist a way to solve a bidirected flow problem by
mapping it to a directed flow problem by using the directed equivalent of the
bidirected graph, described in \Subsection{subsec:directed}.  However, the
calculated flow on a directed edge between, for example, two vertices $f.E \to
g.E$ is not guaranteed to be the same as the flow on $g.B \to f.B$, the edge
that corresponds to the other direction of the implied bidirected edge.  This
problem can be worked around by taking the average of the two counts and using
this as the flow on the bidirected edge.  This approximation is equivalent to
performing monotonization on the binet matrix that represents the linear program
reduction of bidirected flow; this produces a totally unimodular matrix that
represents a linear program that can be solved to find an integral flow that is
at worst a 2-approximation to the optimal integral flow on the bidirected
graph\cite{Medvedev2009}\cite{Hochbaum2004}.
